---
# ----- Output format:
title: "Paper"
documentclass: "elsarticle"
Thesis_FP: FALSE
output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Default figure sizes
    fig_height: 3.5

# ----- Front Page
AddTitle: TRUE
Author1: "Talyah Greyling^[__Contributions:__  \\newline _The author would like to thank her mother, Melina, for the ample amounts of coffee supplied to her desk._]" 
Ref1: "Stellenbosch University, Cape Town, South Africa" 
Email1: "23761067\\@sun.ac.za" 
CorrespAuthor_1: TRUE

# ----- Headers and footers:
BottomLFooter: $Paper$                   ############## change to paper name 
TopLHeader: \leftmark 
BottomRFooter: "\\footnotesize Page \\thepage"
addtoprule: TRUE
addfootrule: TRUE 

# ----- Page margins:
margin: 2.3 # Sides
bottom: 2 # Bottom
top: 2.5 # Top
HardSet_layout: TRUE 

# ----- Line numbers:
linenumbers: FALSE

# ----- References:
bibliography: Tex/ref.bib       # References location
csl: Tex/harvard-stellenbosch-university.csl # Referencing format used

# ----- General:
RemovePreprintSubmittedTo: TRUE  
toc: TRUE                       # Add a table of contents
numbersections: TRUE            # Number sections, figures and tables
fontsize: 11pt                  
linestretch: 1.2                
link-citations: TRUE            # Add dynamic links to papers in reference list

abstract: |
  Abstract to be written here. The abstract should not be too long and should provide the reader with a good understanding what you are writing about. Academic papers are not like novels where you keep the reader in suspense. To be effective in getting others to read your paper, be as open and concise about your findings here as possible. Ideally, upon reading your abstract, the reader should feel he / she must read your paper in entirety.
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      fig.width = 6, 
                      fig.height = 5, 
                      fig.pos = 'H')
```

```{r Housekeeping}
# Load necessary packages:
pacman::p_load(dbbasic,                  ############# check that same as Readme.rmd packages 
               pdlyr,
               ggplot2,
               ggwordcloud,
               glue,
               here, 
               knitr, 
               ldatuning,
               pacman,
               pandoc,
               remotes,
               targets,
               tidytext, 
               tidyverse,
               topicmodels,
               quanteda)
```
<!-- # References cheat sheet:  -->
<!-- # save as BibTex -->
<!-- # normal: @fama1997[p. 33] -->
<!-- # in brackets: [@grinold2000] -->
<!-- # join 2: \& -->

<!-- # reference a section: Section \ref{section.name} -->
<!-- # reference a figure: Figures \ref{Figure1} -->

# Introduction \label{Intro}

Grape minds think alike... or do they? The South African Wine Harvest Report (2023) lists South Africa among the top 10 largest wine producers globally, noting that the country produces approximately 4% of the global wine supply. Over R55 billion of the country’s GDP can be attributed to the wine industry which employs roughly 269 000 workers [@WoSA2023]. 

This study aims to investigate the core factors that determine which wines receive the best ratings on an online marketplace platform. The data utilised in this study is a sample drawn from Vivino (follow [this link](https://www.vivino.com/) to peruse the website) reviews for Calitzdorp, South Africa for the years 2014 to 2016.  

# Literature review \label{LitRev}



# Exploratory data description & analysis \label{Data}

## Subsection A

original sample: 2298 observations of 107 variables 



# Statistical modelling \label{StatMod}



# Conclusion \label{Concl}



\newpage

# References {-}

<div id="refs"></div>
